Minimal trap-spaces of Logical models are maximal siphons of their Petri-net encoding

### 2022-04-29 cmsb22.tex
Header
Some more stuff

\documentclass[runningheads]{llncs}
\usepackage[T1]{fontenc}
% \usepackage{graphicx}
\usepackage{hyperref}
\usepackage{color}
\renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{Minimal trap-spaces of Logical models are maximal siphons of their Petri-net encoding}
\titlerunning{Minimal trap-spaces as maximal siphons}
\author{Van-Giang Trinh\inst{1}\orcidID{0000-1111-2222-3333} \and \\
  Sylvain Soliman\inst{2}\orcidID{0000-0001-5525-7418}}
% \authorrunning{F. Author et al.}

\institute{
  Aix-Marseille Université, Marseille, France\\
  \email{???@lis-lab.fr}\\
  \url{???} \and
  Lifeware team, Inria Saclay center, Palaiseau, France\\
  \email{Sylvain.Soliman@inria.fr}\\
  \url{http://lifeware.inria.fr/~soliman/}
}

@@

\section{Minimal trap-spaces as maximal siphons}
\subsection{Preliminaries}
\subsubsection{Traps-spaces}
\subsubsection{Petri-net encoding of Logical models}
\subsubsection{Siphons}

@@

@@

@@

% \begin{theorem}
% This is a sample theorem. The run-in heading is set in bold, while
% the following text appears in italics. Definitions, lemmas,
% propositions, and corollaries are styled the same way.
% \end{theorem}
% %
% % the environments 'definition', 'lemma', 'proposition', 'corollary',
% % 'remark', and 'example' are defined in the LLNCS documentclass as well.
% %
% \begin{proof}
% Proofs, examples, and remarks have the initial word in italics,
% while the following text appears in normal font.
% \end{proof}
% For citations of references, we prefer the use of square brackets
% and consecutive numbers. Citations using labels or the author/year
% convention are also acceptable. The following bibliography provides
% a sample reference list with entries for journal
% articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
% book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
% and a homepage~\cite{ref_url1}. Multiple citations are grouped
% \cite{ref_article1,ref_lncs1,ref_book1},
% \cite{ref_article1,ref_book1,ref_proc1,ref_url1}.

\subsubsection{Acknowledgments} Please place your acknowledgments at
the end of the paper, preceded by an unnumbered run-in heading (i.e.
3rd-level heading).

\bibliographystyle{splncs04}
\bibliography{cmsb.bib}

>>>>

\documentclass[runningheads]{llncs}
\usepackage[T5]{fontenc}
% \usepackage{graphicx}
\usepackage{hyperref}
\usepackage{color}
\renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{Minimal trap-spaces of Logical models are maximal siphons of their Petri-net encoding}
\titlerunning{Minimal trap-spaces as maximal siphons}
\author{Van-Giang Trịnh\inst{1}\orcidID{0000-0001-6581-998X} \and \\
  Sylvain Soliman\inst{2}\orcidID{0000-0001-5525-7418}}
% \authorrunning{F. Author et al.}

\institute{
  Aix-Marseille Université, Marseille, France\\
  \email{Trinh.Van-Giang@lis-lab.fr}
  \and
  Lifeware team, Inria Saclay center, Palaiseau, France\\
  \email{Sylvain.Soliman@inria.fr}%\\
  %\url{http://lifeware.inria.fr/~soliman/}
}

@@

\section{Minimal trap-spaces as maximal siphons}
\subsection{Preliminaries}
\subsubsection{Traps-spaces}
\subsubsection{Petri-net encoding of Logical models}

Original encoding~\cite{chaouiya2011petri} vs. more recent one~\cite{chatain2014characterization}

\subsubsection{Siphons}

@@

SBML-Qual~\cite{chaouiya2013sbml}/BoolNet~\cite{mussel2010boolnet,klarner2017pyboolnet} to PNML\footnote{\url{https://www.pnml.org/}} works via GINsim/BioLQM~\cite{chaouiya2012logical} with
\begin{verbatim}
\verb|java -jar GINsim.jar -lqm <input.sbml/input.bnet> <output.pnml>|
\end{verbatim}

@@

\subsubsection{Acknowledgments}
Coffee is good, you should drink some!

\bibliographystyle{splncs04}
\bibliography{cmsb22.bib}

@@

% \begin{theorem}
% This is a sample theorem. The run-in heading is set in bold, while
% the following text appears in italics. Definitions, lemmas,
% propositions, and corollaries are styled the same way.
% \end{theorem}
% %
% % the environments 'definition', 'lemma', 'proposition', 'corollary',
% % 'remark', and 'example' are defined in the LLNCS documentclass as well.
% %
% \begin{proof}
% Proofs, examples, and remarks have the initial word in italics,
% while the following text appears in normal font.
% \end{proof}
